An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-15 VLDB2026/main.tex
Update main.tex

%	 修改此处
	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.

>>>>

%	 修改此处
	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods. Unlike other range-filtering algorithms, ACORN is not designed with specialized data structures (such as the $\beta$-WST in WinFilter, the rectangle tree and dynamic segment graph in SeRF, or the HSIG in UNIFY) to achieve efficient range filtering. In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
